---
title: "Clustering tree, a visualisation for examining clusterings a increasing resolutions"
author:
- Luke Zappia (1, 2)
- Alicia Oshlack (1, 2)
date: "1 Bioinformatics, Murdoch Children's Research Institute; 2 School of Biosciences, University of Melbourne"
output:
    bookdown::word_document2:
        reference_docx: style/style.docx
        pandoc_args: [ "--csl", "style/nature.csl" ]
bibliography: style/references.bib
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(autodep        = TRUE,
                      cache          = FALSE,
                      cache.path     = "cache/",
                      cache.comments = TRUE,
                      echo           = FALSE,
                      error          = FALSE,
                      fig.path       = "figures/",
                      fig.width      = 10,
                      fig.height     = 8,
                      dev            = c('png', 'pdf'),
                      message        = FALSE,
                      warning        = FALSE)
```

```{r libaries}
library("clustree")
```

```{r source}

```

```{r palette}

```

```{r load}

```

# Abstract

# Keywords

# Introduction

```{r iris-tree}
data("iris_clusts")

clustree(iris_clusts, prefix = "K")
```

# Methods

# Declarations

## Ethics

Not applicable.

## Availability of data and materials

The clustree package is available from our GitHub repository
(https://github.com/Oshlack/clustree) and the code and datasets used for the
analysis in this paper are available from
https://github.com/Oshlack/clustree-paper.

## Competing interests

The authors declare no competing interests.

## Funding

Luke Zappia is supported by an Australian Government Research Training Program
(RTP) Scholarship. Alicia Oshlack is supported through a National Health and
Medical Research Council Career Development Fellowship APP1126157. MCRI is
supported by the Victorian Government's Operational Infrastructure Support
Program.

## Authors' contributions

## Acknowledgements

# Additional files

# References
